RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-14 paper.tex
yes

% What's the area
Consider the emerging role of a data science team within an
organization.

% How do people do it today?
Individual data scientists and statisticians usually
work on loosely related problems, and must devise effective ways to 
share their findings and to move results from exploratory data analysis
to automated diagnostics and reports deployed for wider consumption.

% Why does this not work?
There are two problems with the current
practice. First, there are gaps in this workflow: EDA is performed
with one set of tools, and automated reports and deployments with another.
Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from easier sharing of
scripts and data feeds, experiments, annotations, and automated
recommendations, which are well beyond what traditional version control
systems provide.

% What are we going to do about this?
\todo{Sell idea, not system} In this paper, we propose RCloud, a system that supports
collaborative data analysis, visualization and web deployment. We will
discuss the design decisions, tradeoffs and limitations, and compare RCloud
to other current proposals.

>>>>

% What's the area
Consider the emerging role of a data science team within an
organization \cite{Keim:2008:VAS}.

% How do people do it today?
Individual data scientists and statisticians usually
work on loosely related problems, and must devise effective ways to 
share their findings and to move results from exploratory data analysis
to automated diagnostics and reports deployed for wider consumption.
They generally rely on a patchwork of resources that are shared informally,
or at best, through systems that attack some of the tasks or functions in
the data analysis workcycle.

% Why does this not work?
There are two problems with the current
practice. First, there are gaps in this workflow:
Exploratory Data Analysis (EDA) is performed with one set of tools,
and automated reports and deployments with another.
Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from easier sharing of
scripts, data sets, data feeds, experiments, annotations, and automated
recommendations, which are well beyond what traditional version control systems provide.

% What are we going to do about this?
\todo{Sell idea, not system} In this paper, we investigate the hypothesis
that the practice of visual analytics can advance by adopting techniques
from information retrieval and collaborative computer, formally supported
within the computing environment. To investigate this, we propose RCloud,
a system that supports collaborative data analysis, visualization and
web deployment. We will discuss the design decisions, tradeoffs and
limitations, and compare RCloud to other current proposals.
